Results_setup

### 2020-04-24 doc/Results_v2.rmd
adjusting values, cleaning up rDatafile

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(kableExtra)
library(ggplot2)
#library(pwr)
library(plyr)
library(lattice)
library(dplyr)
library(raster)
library(lme4)
library(nlme)
library(RLRsim)
library(ggpubr)
library(reshape2)
#library(patchwork)

@@

load(file = "~./MLH1repo/data/Results_setup_4.21.20.RData")

@@

#table( droplevels(female_mouse.avs_for.analysis$strain) )
#there are cast strains too

@@

female.specific.plot <- ggplot(female_mouse.avs_for.analysis, aes(x = as.factor(strain), y = mean_co, color= strain))+ geom_boxplot()+  geom_jitter(aes( alpha=0.5), width = .2 )+ ggtitle("Female mouse av")+scale_color_manual(values=colors_of_strains)+ylim(c(20,34))+
  theme(legend.position="none",
  panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line=element_line(colour = "black"))+theme(axis.text.x = element_text(angle = 45, hjust = 1))

#female.specific.plot

@@

#table( droplevels(just.male_mouse.av$strain) )
#there are cast strains too

#Musc.male_mouse.av <-  just.male_mouse.av %>% filter(sex== "male") %>% filter(subsp == "Musc")

#fomo.male_mouse.av

#male.plot <- ggplot(just.male_mouse.av, aes(x = as.factor(strain), y = mean_co, color= strain))+geom_jitter( alpha=0.5, width = .2) +geom_boxplot()+ ggtitle("Male mouse mean")+scale_color_manual(values=colors_of_strains)+ylim(c(20,34))+theme(legend.position="none",
#  panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
#  panel.background = element_blank(), axis.line=element_line(colour = "black"))+theme(axis.text.x = element_text(angle = 45, hjust = 1))
#male.plot

#musc.male.plot <- ggplot(Musc.male_mouse.av, aes(color= strain))+geom_jitter(aes(x = as.factor(strain), y = mean_co, color= strain, alpha=0.5), width = .2 )+ ggtitle("Musc male of MLH1 distributions")+scale_color_manual(values=colors_of_strains)+ylim(c(20,34))

@@

#Fig1_v1_strain + female.specific.plot - male.plot + plot_layout(ncol=1)
#Fig1_v1_strain / (female.specific.plot + male.plot )

#(p1 | p2 | p3)/p4
```

```{r main.fig1s, echo=FALSE, include=FALSE}
strain.table.HQ_Fig_F <-  strain.table.HQ_Fig %>% filter(sex == "female") %>% filter(strain != "CAST" & strain != "SPRET" & strain != "SPIC" )

@@

To situate variation in recombination rate within an evolutionary framework, we fit a series of models including subspecies, strain, and sex, to mean MLH1 foci counts from `r length(DF.HetC.MixedModel.HQ$mean_co)` mice. We began with a full mixed model (M1, see Methods), which showed that strain 
(random effect p < `r MLH1.MMlmer_results$rand.pval`   **someSmallNumber**), sex (p = `r MLH1.MMlmer_results$sex.results`), subspecies (p=`r MLH1.MMlmer_results$sub.sp`), and subspecies sex (p = `r MLH1.MMlmer_results$interaction.pval`) each significantly affect recombination rate.

@@

We next fit general linear models separately for `r length(fomo.male_mouse.av$mouse)` males and `r length(female_mouse.avs_for.analysis$mouse)` females (M4  **male specific, M2? rename the code for these models**). In the male dataset, three strains significantly affect recombination rate: musculus^PWD^ ((glm; p = `r sum_MLH1.male.specific.glm.M2$coefficients[5,][4]`; effect = 
`r MLH1.male.specific.glm.M2$coefficients[5]` -- ~ 5 foci), and musculus^SKIVE^ (glm; p = 0.01; `r sum_MLH1.male.specific.glm.M2$coefficients[8,][4]` -- effect = `r MLH1.male.specific.glm.M2$coefficients[8]` -- ~7 foci), and  _molossinus^MSM^_ (glm; p=`r sum_MLH1.male.specific.glm.M2$coefficients[6,][4]`; effect  `r MLH1.male.specific.glm.M2$coefficients[6]` ~ 2 foci). These three strains point to rapid evolution in recombination rate in spermatocytes; we subsequently refer to them collectively as "high-recombination" strains.  Analysis of the female dataset points to four strains with significant effects on recombination rate: domesticus^G^ (p = `r sum_MLH1.female.spc.glm.M2$coefficients[2,][4]`), molossinus^MSM^ (p = `r sum_MLH1.female.spc.glm.M2$coefficients[5,][4]`), domesticus^LEW^ (p = `r sum_MLH1.female.spc.glm.M2$coefficients[3,][4]`), and musculus^PWD^ (p= `r sum_MLH1.female.spc.glm.M2$coefficients[4,][4]`). Strain effect sizes in females are modest in magnitude (ranging from 1 to 4 foci) compared to those in males.

@@

The high-recombination strains have significantly more DMC1 foci than the low-recombination strains in early zygotene cells (t-test, p<**someSmallNumber** -- `r ttest.HighLow.L.pval`). In contrast, the two strain groups do not differ in DMC1 foci counted in late zygotene cells (t-test, p = 0.66 --- `r ttest.HighLow.Z.pval`).

@@

```{r with.cow, echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}
library(cowplot)

top.triangle <- function() {
  plot( PER_Foci_2 ~ PER_Foci_1, data = (Curated_BivData %>% filter(sex == "female") %>% filter(hand.foci.count == 2) %>% filter(subsp == "Dom") ), 
      axes = FALSE, ylab = 'Foci2', xlab = NA, main='Foci1',
      xlim=c(0,1), ylim=c(0,1),  xaxt="n", yaxt="n" )
  axis(side = 2, las = 1, pos=0)
  axis(side = 3, las = 1, pos=1)
  abline(coef = c(0,1))
}

bottom.triangle <- function() {
  plot( PER_Foci_1 ~ PER_Foci_2, data = (Curated_BivData %>% filter(sex == "female") %>% filter(hand.foci.count == 2) %>% filter(subsp == "Dom") ), 
      axes = FALSE, xlab = NA, ylab = NA, xlim=c(0,1), ylim=c(0,1),  xaxt="n", yaxt="n" )
  axis(side = 1, las = 1, pos=0)
  axis(4, las = 1, pos=1) #flip label to right side
  abline(coef = c(0,1))
}

```{r another.triangle, echo=FALSE, fig.width = 5, fig.height=5, eval=FALSE}

Curated_BivData <- Curated_BivData %>% filter(PER_Foci_2 < 1.01)

with( (Curated_BivData %>% filter(strain == "G") ), { 
  plot(  c( (Curated_BivData %>% filter(sex == "male") %>% filter(strain == "G") %>% filter(hand.foci.count == 2))$PER_Foci_2,
              (Curated_BivData %>% filter(strain == "G") %>% filter(sex == "female") %>% filter(hand.foci.count == 2))$PER_Foci_1),

                     c(   (Curated_BivData %>% filter(sex == "male") %>% filter(strain == "G") %>% filter(hand.foci.count == 2) )$PER_Foci_1,

                       (Curated_BivData %>% filter(strain == "G") %>% filter(sex == "female") %>% filter(hand.foci.count == 2) )$PER_Foci_2), 
          xlab = "Position1", ylab = "Position2", asp = 1, main="G IFD distributions"); 
  axis(4, las = 1, pos=1); #right side
  axis(side = 3, las = 1, pos=1); #
  segments(0, 0, 1, 1); abline(v = 0:1, h = 0:1) })

reverse the axis

```{r updated.triangl.plots, echo=FALSE, message=FALSE, warning=FALSE}
my.data <- data.frame(my.x=c(.2, .4, .6, .1), my.y=c(.3, .5, .7, .9))
x.dist <- .5
my.data.2 <- transform(my.data, my.y=my.y + x.dist)

#x_dist is a value for spacing the trianlges, remeber that the data values need
#to be adjusted as well
#the rest of the positions are slightly off

#make a loop to enter/push the merge triangles into a empty list

#Top is female
top.triangle2 <- function() {
  #top-y position is male Pos2
  plot(  (Curated_BivData %>% filter(strain == "KAZ") %>% filter(sex == "female") %>% filter(hand.foci.count == 2) )$PER_Foci_2 ~ 
    #top-x position is female Pos1     
    (Curated_BivData %>% filter(strain == "KAZ") %>% filter(sex == "female") %>% filter(hand.foci.count == 2) )$PER_Foci_1,

       data= (Curated_BivData %>% filter(sex == "female") %>% filter(strain == "KAZ") %>% filter(hand.foci.count == 2) ), 
       col =  "coral4",
       axes=FALSE, ylab='', xlab="", 
       main='', xlim=c(0, 1), ylim=c(0, 1), xaxt="n", yaxt="n", asp=1)
  mtext("KAZ IFD Distributions", 3, 5, font=2, cex=1.3, adj=.5)

  mtext("Female Position.2", 2, .75)
  mtext("Female Position.1", 3, 2)
  axis(side=2, las=1, pos=0)
  axis(side=3, las=1, pos=1)
  lines(0:1, 0:1)
}

#bottom is male
bottom.triangle2 <- function() {
    #bottom-y position is male Pos1
  points(  (Curated_BivData %>% filter(strain == "KAZ") %>% filter(sex == "male") %>% filter(hand.foci.count == 2) )$PER_Foci_1 ~ 
    #bottom-x position is male Pos2     
    (Curated_BivData %>% filter(strain == "KAZ") %>% filter(sex == "male") %>% filter(hand.foci.count == 2) )$PER_Foci_2,

         data=(Curated_BivData %>% filter(sex == "male") %>% filter(strain == "KAZ") %>% filter(hand.foci.count == 2) ),

    col =  "coral4",
         xpd=TRUE)
  mtext("Male Position.2", 1, 1.5, at=mean(par()$usr[1:2])) #  + x.dist
  mtext("Male Position.1", 4, 3)#, padj=par()$usr[1]
  x.at <- axisTicks(par()$usr[1:2], 0) #+ x.dist
  axis(side=1, las=1, pos=0, at=x.at, 
       labels=F, xpd=TRUE)
  mtext(seq(0, 1, .2), 1, 0, at=x.at)
  axis(4, las=1, pos=1) # + x.dist
  lines(0:1, 0:1, xpd=TRUE)# + x.dist

  }

png("~./MLH1repo/doc/figureFiles/KAZ.triangle.png", width=650, height=500)
op <- par(mar=c(3, 4, 8, 12) + 0.1, oma=c(2, 0, 0, 2))
top.triangle2()
bottom.triangle2()
par(op)
dev.off()

```{r auto.loop.ifd, echo=FALSE}

#don't think I need this loop
for(i in 1:length(auto_curate_DF$strain )){
  auto_curate_DF$quant_status[i] <- ifelse( is.element(auto_curate_DF$strain[i], exclude_mice_list), "exclude", NA)
  }

@@

for(i in 1:(length(df_strain_list))){
  current.strain <- as.character(df_strain_list[[i]]$strain[1])
  #declare file
  png(paste0("~./MLH1repo/doc/figureFiles/test.triangle_", current.strain, ".png"),  width=650, height=500)

  #Top is female
top.triangle2 <- function() {
  #top-y position is male Pos2
  plot(  (Curated_BivData %>% filter(strain == current.strain  ) %>% filter(sex == "female") %>% filter(hand.foci.count == 2) )$PER_Foci_2 ~ 
    #top-x position is female Pos1     
    (Curated_BivData %>% filter(strain == current.strain   ) %>% filter(sex == "female") %>% filter(hand.foci.count == 2) )$PER_Foci_1,

       data= (Curated_BivData %>% filter(sex == "female") %>% filter(strain == current.strain) %>% filter(hand.foci.count == 2) ), 
       col =  colors_of_strains[current.strain],
       axes=FALSE, ylab='', xlab="", 
       main= "IFD Distribution",  xlim=c(0, 1), ylim=c(0, 1), xaxt="n", yaxt="n", asp=1)

  mtext(current.strain, 3, 5, font=2, cex=1.3, adj=.5)

  mtext("Female Position.2", 2, .75)
  mtext("Female Position.1", 3, 2)
  axis(side=2, las=1, pos=0)
  axis(side=3, las=1, pos=1)
  lines(0:1, 0:1)
  }

bottom.triangle2 <- function() {
    #bottom-y position is male Pos1
  points(  (Curated_BivData %>% filter(strain == current.strain) %>% filter(sex == "male") %>% filter(hand.foci.count == 2) )$PER_Foci_1 ~ 
    #bottom-x position is male Pos2     
    (Curated_BivData %>% filter(strain == current.strain) %>% filter(sex == "male") %>% filter(hand.foci.count == 2) )$PER_Foci_2,

         data=(Curated_BivData %>% filter(sex == "male") %>% filter(strain == current.strain) %>% filter(hand.foci.count == 2) ),

    col =  colors_of_strains[current.strain], #this might not be working right
         xpd=TRUE)
  mtext("Male Position.2", 1, 1.5, at=mean(par()$usr[1:2])) #  + x.dist
  mtext("Male Position.1", 4, 3)#, padj=par()$usr[1]
  x.at <- axisTicks(par()$usr[1:2], 0) #+ x.dist
  axis(side=1, las=1, pos=0, at=x.at, 
       labels=F, xpd=TRUE)
  mtext(seq(0, 1, .2), 1, 0, at=x.at)
  axis(4, las=1, pos=1) # + x.dist
  lines(0:1, 0:1, xpd=TRUE)# + x.dist

  }

  op <- par(mar=c(3, 4, 8, 12) + 0.1, oma=c(2, 0, 0, 2))
  top.triangle2()
  bottom.triangle2() #not working
  par(op)
  dev.off()
  }

```{r Q1.IFD_load.triangles, echo=FALSE, message=FALSE, warning=FALSE}

@@

G.triangle.png <- readPNG("~./MLH1repo/doc/figureFiles/G.triangle.png")
WSB.triangle.png <- readPNG("~./MLH1repo/doc/figureFiles/WSB.triangle.png")
LEW.triangle.png <- readPNG("~./MLH1repo/doc/figureFiles/LEW.triangle.png")

@@

G.triangle.ggplot <- ggplot(empty.DF, aes(x = col1, y = col2)) +
  background_image(G.triangle.png) + theme(axis.title.x=element_blank(),
 axis.text.x=element_blank(),axis.ticks.x=element_blank(),axis.title.y=element_blank(),
                                  axis.text.y=element_blank(),axis.ticks.y=element_blank() )

LEW.triangle.ggplot <- ggplot(empty.DF, aes(x = col1, y = col2)) +
  background_image(LEW.triangle.png) + theme(axis.title.x=element_blank(),
 axis.text.x=element_blank(),axis.ticks.x=element_blank(),axis.title.y=element_blank(),
                                  axis.text.y=element_blank(),axis.ticks.y=element_blank() )

library("cowplot")
fig1  <- ggdraw() +
  draw_plot(WSB.triangle.ggplot, x=0, y=0, width=.45, height=.45) +
  draw_plot(G.triangle.ggplot,   x=0, y=.4, width=.45, height=.45) +
  draw_plot(LEW.triangle.ggplot, x=0, y=.6, width=.45, height=.45)

fig1

>>>>

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(kableExtra)
library(ggplot2)
#library(pwr)
library(plyr)
library(lattice)
library(dplyr)
library(raster)
library(lme4)
library(nlme)
library(RLRsim)
library(ggpubr)
library(reshape2)
library(patchwork)

@@

load(file = "~./MLH1repo/data/Results_setup_4.24.20.RData")

@@

@@

female.specific.plot <- ggplot(female_mouse.avs_for.analysis, aes(x = as.factor(strain), y = mean_co, color= strain))+ geom_boxplot()+  geom_jitter(aes( alpha=0.5), width = .2 )+ ggtitle("Female mouse av")+scale_color_manual(values=colors_of_strains)+ylim(c(20,34))+
  theme(legend.position="none",
      axis.text.x=element_blank(), axis.title.x = element_blank(), axis.ticks.x = element_blank(),
  panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line=element_line(colour = "black"))

#+theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

#table( droplevels(just.male_mouse.av$strain) )
#there are cast strains too
#Musc.male_mouse.av <-  just.male_mouse.av %>% filter(sex== "male") %>% filter(subsp == "Musc")
#fomo.male_mouse.av

male.plot <- ggplot(just.male_mouse.av, aes(x = as.factor(strain), y = mean_co, color= strain))+geom_jitter( alpha=0.5, width = .2) +geom_boxplot()+ ggtitle("Male mouse mean")+scale_color_manual(values=colors_of_strains)+ylim(c(20,34))+
  theme(legend.position="none", axis.text.x=element_blank(), axis.title.x = element_blank(), axis.ticks.x = element_blank(), 
  panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line=element_line(colour = "black"))

#+theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

#Fig1_v1_strain + female.specific.plot - male.plot + plot_layout(ncol=1)
Fig1_v1_strain / (female.specific.plot + male.plot )

```{r main.fig1s, echo=FALSE}
strain.table.HQ_Fig_F <-  strain.table.HQ_Fig %>% filter(sex == "female") %>% filter(strain != "CAST" & strain != "SPRET" & strain != "SPIC" )

@@

To situate variation in recombination rate within an evolutionary framework, we fit a series of models including subspecies, strain, and sex, to mean MLH1 foci counts from `r length(DF.HetC.MixedModel.HQ$mean_co)` mice. We began with a full mixed model (M1, see Methods), which showed that strain 
(random effect p < `r MLH1.MMlmer_results$rand.pval` -- `r 1/1000000` someSmallNumber), sex (p = `r MLH1.MMlmer_results$sex.results`), subspecies (p=`r MLH1.MMlmer_results$sub.sp`), and subspecies sex (p = `r MLH1.MMlmer_results$interaction.pval`) each significantly affect recombination rate.

@@

We next fit general linear models separately for `r length(fomo.male_mouse.av$mouse)` males and `r length(female_mouse.avs_for.analysis$mouse)` females (M4  **male specific, M2? rename the code for these models**).

In the male dataset, three strains significantly affect recombination rate: musculus^PWD^ ((glm; p = `r sum_MLH1.male.glm.M4$coefficients[5,][8]`; effect = 
`r sum_MLH1.male.glm.M4$coefficients[8]` -- ~ 5 foci), and 
musculus^SKIVE^ (glm; p = 0.01; `r sum_MLH1.male.glm.M4$coefficients[5,][10]` -- effect = `r sum_MLH1.male.glm.M4$coefficients[10]` -- ~2 foci), and  _molossinus^MSM^_ (glm; p=`r sum_MLH1.male.glm.M4$coefficients[5,][9]`; effect  `r sum_MLH1.male.glm.M4$coefficients[9]` ~ 7 foci).

These three strains point to rapid evolution in recombination rate in spermatocytes; we subsequently refer to them collectively as "high-recombination" strains.  Analysis of the female dataset points to four strains with significant effects on recombination rate: domesticus^G^ (p = `r sum_MLH1.female.spc.glm.M2$coefficients[2,][4]`), molossinus^MSM^ (p = `r sum_MLH1.female.spc.glm.M2$coefficients[5,][4]`), domesticus^LEW^ (p = `r sum_MLH1.female.spc.glm.M2$coefficients[3,][4]`), and musculus^PWD^ (p= `r sum_MLH1.female.spc.glm.M2$coefficients[4,][4]`). Strain effect sizes in females are modest in magnitude (ranging from 1 to 4 foci) compared to those in males.

@@

The high-recombination strains have significantly more DMC1 foci than the low-recombination strains in early zygotene cells (t-test, p< someSmallNumber -- `r 1/1000000` -- `r ttest.HighLow.L.pval`). In contrast, the two strain groups do not differ in DMC1 foci counted in late zygotene cells (t-test, p = 0.66 --- `r ttest.HighLow.Z.pval`).

@@

```{r triangle.IFD.auto.loop.ifd, echo=FALSE, eval=FALSE}

#Top is female
top.triangle2 <- function() {
  #top-y position is male Pos2
  plot(  (Curated_BivData %>% filter(strain == "WSB"  ) %>% filter(sex == "female") %>% filter(hand.foci.count == 2) )$PER_Foci_2 ~ 
    #top-x position is female Pos1     
    (Curated_BivData %>% filter(strain == "WSB"   ) %>% filter(sex == "female") %>% filter(hand.foci.count == 2) )$PER_Foci_1,

       data= (Curated_BivData %>% filter(sex == "female") %>% filter(strain == "WSB") %>% filter(hand.foci.count == 2) ), 
       col =  colors_of_strains["WSB"],
       axes=FALSE, ylab='', xlab="", 
       main= "IFD Distribution",  xlim=c(0, 1), ylim=c(0, 1), xaxt="n", yaxt="n", asp=1)

  mtext("WSB", 3, 5, font=2, cex=1.3, adj=.5)
  mtext("Female Position.2", 2, .75)
  mtext("Female Position.1", 3, 2)
  axis(side=2, las=1, pos=0)
  axis(side=3, las=1, pos=1)
  lines(0:1, 0:1)
  }

bottom.triangle2 <- function() {
    #bottom-y position is male Pos1
  points(  (Curated_BivData %>% filter(strain == "WSB") %>% filter(sex == "male") %>% filter(hand.foci.count == 2) )$PER_Foci_1 ~ 
    #bottom-x position is male Pos2     
    (Curated_BivData %>% filter(strain == "WSB") %>% filter(sex == "male") %>% filter(hand.foci.count == 2) )$PER_Foci_2,

         data=(Curated_BivData %>% filter(sex == "male") %>% filter(strain == "WSB") %>% filter(hand.foci.count == 2) ),

    col =  colors_of_strains["WSB"], xpd=TRUE)
  mtext("Male Position.2", 1, 1.5, at=mean(par()$usr[1:2])) #  + x.dist
  mtext("Male Position.1", 4, 3)#, padj=par()$usr[1]
  x.at <- axisTicks(par()$usr[1:2], 0) #+ x.dist
  axis(side=1, las=1, pos=0, at=x.at, labels=F, xpd=TRUE)
  mtext(seq(0, 1, .2), 1, 0, at=x.at)
  axis(4, las=1, pos=1) # + x.dist
  lines(0:1, 0:1, xpd=TRUE)# + x.dist
  }

#par(mar=c(1,1,1,1))
op <- par(mar=c(3, 4, 8, 12) + 0.1, oma=c(2, 0, 0, 2))
plot(top.triangle2(), bottom.triangle2() ) #not working
par(op)
dev.off()

```{r double.tri.rewrite, echo=FALSE, eval=FALSE}
#good function, saves to file, can't reproduce in rmd

@@

#this works
top.triangle2 <- function(my.y, my.x, my.data) {
  plot(my.y ~ my.x, data= my.data, axes=FALSE, ylab='', xlab="", 
       main='', xlim=c(0, 1), ylim=c(0, 1), xaxt="n", yaxt="n", asp=1,
       col =  colors_of_strains[current.strain])
  mtext(current.strain, 3, 5, font=2, cex=1.3, adj=.95)
  mtext("Position.2.Female", 2, .75)
  mtext("Position.1.Female", 3, 2)
  axis(side=2, las=1, pos=0)
  axis(side=3, las=1, pos=1)
  lines(0:1, 0:1)
}

bottom.triangle2 <- function(my.y, my.x, my.data){
  points(my.x ~ my.y, data=my.data, xpd=TRUE, 
          col =  colors_of_strains[current.strain])

  mtext("Position.2.Male", 1, 1.5, at=mean(par()$usr[1:2]) + x.dist)
  mtext("Position.1.Male", 4, 3, padj=par()$usr[1] + 10)
  x.at <- axisTicks(par()$usr[1:2], 0) + x.dist
  axis(side=1, las=1, pos=0, at=x.at, 
       labels=F, xpd=TRUE)
  mtext(seq(0, 1, .2), 1, 0, at=x.at)
  axis(4, las=1, pos=1 + x.dist)
  lines(0:1 + x.dist, 0:1, xpd=TRUE)
}

x.dist <- .5

for(i in 1:(length(df_strain_list))){
  print(i)
  current.strain <- as.character(df_strain_list[[i]]$strain[1])

  #declare file
  png(paste0("~./MLH1repo/doc/figureFiles/test.triangle_", current.strain, ".png"),  width=650, height=500)

  my.data = (Curated_BivData %>% filter(strain == current.strain) %>% filter(hand.foci.count == 2) )

  my.x.top = (Curated_BivData %>% filter(strain == current.strain) %>% filter(sex == "female") %>% filter(hand.foci.count == 2) )$PER_Foci_1

  my.y.top = (Curated_BivData %>% filter(strain == current.strain) %>% filter(sex == "female") %>% filter(hand.foci.count == 2) )$PER_Foci_2

  my.x.bottom = (Curated_BivData %>% filter(strain == current.strain) %>% filter(sex == "male") %>% filter(hand.foci.count == 2) )$PER_Foci_1

  my.y.bottom = (Curated_BivData %>% filter(strain == current.strain) %>% filter(sex == "male") %>% filter(hand.foci.count == 2) )$PER_Foci_2

  op <- par(mar=c(3, 4, 8, 12) + 0.1, oma=c(2, 0, 0, 2))
  top.triangle2(my.y.top, my.x.top, my.data)
  bottom.triangle2(my.y.bottom+x.dist, my.x.bottom, my.data) #x.dist
  par(op)
  dev.off()
}

```{r Q1.IFD_load.triangles, echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "Example of Sex differences in IFD distributions"}

@@

#load all the files / arrange the plots from above 
WSB.triangle.png <- readPNG("~./MLH1repo/doc/figureFiles/test.triangle_WSB.png")

@@

#show wsb as example
WSB.triangle.ggplot

#library("cowplot")
#fig1  <- ggdraw() +
#  draw_plot(WSB.triangle.ggplot, x=0, y=0, width=.45, height=.45) +
#  draw_plot(G.triangle.ggplot,   x=0, y=.4, width=.45, height=.45) +
#  draw_plot(LEW.triangle.ggplot, x=0, y=.6, width=.45, height=.45)

### 2020-04-24 src/Result_Setup.Rmd
adjusting values, cleaning up rDatafile

```{r Male.specific.glm, echo=FALSE}
# 1 way anova, is at least 1 strain different from the rest?
# given a lm, how sig is the strain effect
glm.male.strain.subsp <- glm(mean_co ~ subsp * strain, data= just.male_mouse.av)

#summry.male.strain.effects <- summary(glm.male.strain.subsp)
#round(summry.male.strain.effects$coefficients[,c(1,4)], 5)

@@

#1. determine which strain effects are sig

#M2
MLH1.male.specific.glm.M2 <- glm(mean_co ~ strain, data= just.male_mouse.av)
sum_MLH1.male.specific.glm.M2 <- summary(MLH1.male.specific.glm.M2)

@@

#even when all the other male strains are added -- the same result; PWD, MSM and SKIVE strain effects are significant.
```

```{r MALE.SPECIFIC.variance.model, echo=FALSE}
## within mouse variance models 
lmVAR.male.strain.subsp <- lm(var ~ subsp * strain, data= just.male_mouse.av)
summry.male.strain.VAReffects <- summary(lmVAR.male.strain.subsp)
#round(summry.male.strain.VAReffects$coefficients[,c(1,4)], 5)

#all p values kinda high, MSM and TOM are slightly sig
lmVAR.male.strain <- lm(var ~ strain, data= just.male_mouse.av)
lmVAR.male.strain_sum <- summary(lmVAR.male.strain)
#round(lmVAR.male.strain_sum$coefficients[,c(1,4)], 5)
#non sig

lmcv.male.strain <- lm(cV ~ strain, data= just.male_mouse.av)
lmcv.male.strain_sum <- summary(lmcv.male.strain)
#round(lmcv.male.strain_sum$coefficients[,c(1,4)], 5)
#HMI sig for cv model -- in the other model, CAST subsp and TOM strain are slightly significant

@@

lm.m1.Q12_male <- lm(var ~ subsp * strain, data= Q12_male_table)
lm.m1.Q12_male_sum <- summary(lm.m1.Q12_male)
#round(lm.m1.Q12_male_sum$coefficients[,c(1,4)], 5)
#NS

lm.m2.Q12_male <- lm(var ~ strain, data= Q12_male_table)
lm.m2.Q12VAR.male_sum <- summary(lm.m2.Q12_male)
#round(lm.m2.Q12VAR.male_sum$coefficients[,c(1,4)], 5)
#NS

@@

set up, t.tests, correlations

```{r DMC1.setup, echo=FALSE}
#load DMC1 csv
#DMC1.DF <- read.csv("~./DMC1/newJuviQuant.csv", header = TRUE)
DMC1.DF <- read.csv("~./MLH1repo/data/DMC1newJuviQuant.csv", header = TRUE)

@@

DMC1.target.strains <- subset(mean.MLH1.obs, category == "G male" |
                   category == "WSB male" |
                     category == "KAZ male" |
                  category == "MSM male" |
                    category == "PWD male")
#attach this mini DF to the DMC1 data

```{r DMC1_t.tests, echo=FALSE, warning=FALSE}
#2. t-tests for the DMC1 counts 
#need to account for sample sizes when comparing t.tests (KAZ and G don't have equal across )
#best case scnario -- more microscoping to get ~20 cells for each stage by strain combo

@@

```{r DMC1.rand.calq, echo=FALSE}

@@

```{r DMC1.ratios, echo=FALSE}

@@

```{r DMC1.setup, echo=FALSE}
#load DMC1 csv
#DMC1.DF <- read.csv("~./DMC1/newJuviQuant.csv", header = TRUE)
DMC1.DF <- read.csv("~./MLH1repo/data/DMC1newJuviQuant.csv", header = TRUE)

@@

```{r MAIN.DMC1.plot, echo=FALSE, warning=FALSE}
#think of better color scheme
#make the jitter col thinner or make the stacked dots.
#remember that box-plots add outlier dots.
#change y labels

@@

```{r plot.stage.ttest, echo=FALSE, warning=FALSE}

@@

```{r DMC1_t.tests, echo=FALSE, warning=FALSE}
#2. t-tests for the DMC1 counts 
#need to account for sample sizes when comparing t.tests (KAZ and G don't have equal across )
#best case scnario -- more microscoping to get ~20 cells for each stage by strain combo

@@

```{r Save.File, echo=FALSE}
#save Rdata
save.image("~./MLH1repo/data/Results_setup_4.21.20.RData")

>>>>

```{r Male.specific.glm, echo=FALSE}

#these are M4
#M4
MLH1.male.glm.M4 <- glm(mean_co ~ subsp * strain, data= just.male_mouse.av)
sum_MLH1.male.glm.M4 <- summary(MLH1.male.glm.M4)
#round(summry.male.strain.effects$coefficients[,c(1,4)], 5)

#sum_MLH1.male.specific.glm.M2$coefficients[5,][4]

#PWD, SKIVE, MSM
#8,9,10

@@

#M4.2
MLH1.male.glm.M4.2 <- glm(mean_co ~ strain, data= just.male_mouse.av)
sum_MLH1.male.glm.M4.2 <- summary(MLH1.male.glm.M4.2)

@@

```{r MALE.SPECIFIC.variance.model, echo=FALSE}
## within mouse variance models 
lmVAR.male.strain.subsp <- glm(var ~ subsp * strain, data= just.male_mouse.av)
summry.male.strain.VAReffects <- summary(lmVAR.male.strain.subsp)
#round(summry.male.strain.VAReffects$coefficients[,c(1,4)], 5)

#all p values kinda high, MSM and TOM are slightly sig
lmVAR.male.strain <- glm(var ~ strain, data= just.male_mouse.av)
lmVAR.male.strain_sum <- summary(lmVAR.male.strain)
#round(lmVAR.male.strain_sum$coefficients[,c(1,4)], 5)
#non sig

lmcv.male.strain <- glm(cV ~ strain, data= just.male_mouse.av)
lmcv.male.strain_sum <- summary(lmcv.male.strain)
#round(lmcv.male.strain_sum$coefficients[,c(1,4)], 5)
#HMI sig for cv model -- in the other model, CAST subsp and TOM strain are slightly significant

@@

lm.m1.Q12_male <- glm(var ~ subsp * strain, data= Q12_male_table)
lm.m1.Q12_male_sum <- summary(lm.m1.Q12_male)
#round(lm.m1.Q12_male_sum$coefficients[,c(1,4)], 5)
#NS

lm.m2.Q12_male <- glm(var ~ strain, data= Q12_male_table)
lm.m2.Q12VAR.male_sum <- summary(lm.m2.Q12_male)
#round(lm.m2.Q12VAR.male_sum$coefficients[,c(1,4)], 5)
#NS

@@

set up, t.tests, correlations, says there are duplicate titles

```{r DMC1.setup1, echo=FALSE}
#load DMC1 csv
#DMC1.DF <- read.csv("~./DMC1/newJuviQuant.csv", header = TRUE)
DMC1.DF <- read.csv("~./MLH1repo/data/DMC1newJuviQuant.csv", header = TRUE)

@@

DMC1.target.strains <- subset(mean.MLH1.obs, category == "G male" |
                   category == "WSB male" |
                     category == "KAZ male" |
                  category == "MSM male" |
                    category == "PWD male")
#attach this mini DF to the DMC1 data
```

```{r DMC1_t.tests1, echo=FALSE, warning=FALSE}
#2. t-tests for the DMC1 counts 
#need to account for sample sizes when comparing t.tests (KAZ and G don't have equal across )
#best case scnario -- more microscoping to get ~20 cells for each stage by strain combo

@@

```{r DMC1.rand.calq1, echo=FALSE}

@@

```{r DMC1.ratios1, echo=FALSE}

@@

```{r DMC1.setup, echo=FALSE, eval=FALSE}
#load DMC1 csv
#DMC1.DF <- read.csv("~./DMC1/newJuviQuant.csv", header = TRUE)
DMC1.DF <- read.csv("~./MLH1repo/data/DMC1newJuviQuant.csv", header = TRUE)

@@

```{r MAIN.DMC1.plot, echo=FALSE, warning=FALSE, eval=FALSE}
#think of better color scheme
#make the jitter col thinner or make the stacked dots.
#remember that box-plots add outlier dots.
#change y labels

@@

```{r plot.stage.ttest, echo=FALSE, warning=FALSE, eval=FALSE}

@@

```{r DMC1_t.tests, echo=FALSE, warning=FALSE, eval=FALSE}
#2. t-tests for the DMC1 counts 
#need to account for sample sizes when comparing t.tests (KAZ and G don't have equal across )
#best case scnario -- more microscoping to get ~20 cells for each stage by strain combo

@@

```{r Save.File, echo=FALSE}
#save Rdata
save.image("~./MLH1repo/data/Results_setup_4.24.20.RData")
